\documentclass[12pt]{article}
\usepackage{mycv}
\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty}
\iffalse
\begin{center}
    {\huge\bfseries ENEOJO RICHARD AMOBEDA}\\
    \vspace{0.5cm}
    \textcolor{orange}{\faMapMarker} \fontfmt{5/3 71 Glenavon Road}\\
    \fontfmt{Glasgow, Lanarkshire, G20 0HR}\\[5pt]
    \textcolor{orange}{\faEnvelopeO} amobedarichard@gmail.com\\[5pt]
    \textcolor{orange}{\faPhone} +447742098091\\
\end{center}
\fi

%\iffalse
\begin{center}
    {\huge\bfseries ENEOJO RICHARD AMOBEDA}\\
    \vspace{0.5cm}
    \textcolor{orange}{\faMapMarker} \fontfmt{85 White Eagle Road, Swindon, Wiltshire, SN25 1PY}\\[5pt]
    \textcolor{orange}{\faEnvelopeO} ramobeda@rocketmail.com\\[5pt]
    \textcolor{orange}{\faPhone} +447742098091\\
\end{center}
%\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\heading{professional summary}
\parbox{0.8\textwidth}{
Motivated and detail-oriented Junior Frontend Developer with a passion for building responsive and user-friendly web applications. Strong foundation in HTML, CSS, JavaScript, and experience working with frameworks like React and Vite.js. Eager to contribute technical skills and creativity to a dynamic development team.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\heading{education}
\qualification{M.Sc. Computer Science (2025)}{University of Lincoln, Lincolnshire, United Kingdom}\\[5pt]

\qualification{B.Sc. Computer Sc./Mathematics (2019)}{University of Agriculture, Makurdi, Nigeria}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\heading{skills}
\parbox{0.9\textwidth}{
%\begin{multicols}{2}
\begin{itemize}
%\item[\maltese] Machine Learning
%\item[\maltese] Computer vision
\item[\maltese] HTML, CSS, JavaScript (ES6+)
\item[\maltese] Responsive web design \& CSS frameworks (Bootstrap, SACSS)
\item[\maltese] JavaScript frameworks (React.js, Vite.js)
\item[\maltese] Version control (Git, GitHub)
\end{itemize}
%\end{multicols}
}

\heading{Projects}
\begin{description}
    \item[A Real Estate Website: –] Developed a responsive Real Estate with interactive UI elements.
    \item[Portfolio Website: -] Built a personal portfolio showcasing projects and skills.
    \item[E-commerce Website: –] Developed a responsive online store with interactive UI elements.
\end{description}



\iffalse


\heading{Reference}
{\bf Declan Mackenzie}\\ 
{\em Recruitment Consultant}\\
SRS Partnership Limited\\
Pentagon Centre, 38 Washington Street, Glasgow, G3 8AZ, Room 122 (first floor)\\
\textcolor{orange}{\faPhone} 0141 212 1111\qquad
\textcolor{orange}{\faEnvelopeO} declan@srspartnership.com\\

 {\bf Ann Karomo}\\ 
 {\em Manager}\\
Serene HealthCare Services LTD\\
109 Stratton Road, SN1 2NY Swindon\\
\textcolor{orange}{\faPhone} +447389142266\qquad
\textcolor{orange}{\faEnvelopeO} info@sereneservices.co.uk\\

{\bf Miss Khadija}\\ 
{\em Manager}\\
KAEDI Recruitment Agency Ltd\\
Dancastle Court Unit 10, Arcadia Avenue, London, England, N3 2JU\\
\textcolor{orange}{\faPhone} +447376901434\qquad
\textcolor{orange}{\faEnvelopeO} khadija@kaedirecruitment.co.uk 
\fi
\end{document}
